SSA based global code motion of identical computations

### 2017-04-17 acmart-pacmpl-template.tex
adding codesize and spills

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|c|c|}
      \hline
      Metric               & Before & After              \\\hline
      Call sites deleted, not inlined             & 1988    & 1988   \\\hline
      Functions deleted (all callers found)       & 38250   & 38255  \\\hline
      Functions inlined                           & 154986  & 154985 \\\hline
      Allocas merged together                     & 212     & 212    \\\hline
      Caller-callers analyzed                     & 193042  & 193092 \\\hline
      Call sites analyzed                         & 414336  & 414381 \\\hline
      Rematerialized defs for spilling            & 18321   & 18326  \\\hline
      Rematerialized defs for splitting           & 5719    & 5842   \\\hline
      Spill slots allocated                       & 42912   & 42970  \\\hline
      Spilled live ranges                         & 61330   & 61362  \\\hline
      Spills inserted                             & 50724   & 50784  \\\hline
\end{tabular}
  \end{center}
  \caption{Static metrics before and after code-hoisting on \LLVMTestSuite{}}
  \label{tab:static-results}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|c|c|c|}
      \hline
Number of spills                &base   &code-motion &\%loss \\\hline
400.perlbench	&2542	&2481	&0.97\\\hline
401.bzip2	        &718	&707	&0.98\\\hline
403.gcc	        &5778	&5710	&0.98\\\hline
429.mcf	        &14	&17	&1.21\\\hline
433.milc	        &616	&624	&1.01\\\hline
444.namd	        &3185	&3223	&1.01\\\hline
445.gobmk	        &2166	&2170	&1.00\\\hline
447.dealII	        &10038	&9151	&0.91\\\hline
450.soplex	        &1104	&1114	&1.00\\\hline
453.povray	        &5199	&5176	&0.99\\\hline
456.hmmer	        &1195	&1195	&1   \\\hline
458.sjeng	        &168	&169	&1.00\\\hline
462.libquantum	&183	&183	&1   \\\hline
464.h264ref	&3382	&3423	&1.01\\\hline
470.lbm	        &30	&30	&1   \\\hline
471.omnetpp	&521	&522	&1.00\\\hline
473.astar	        &176	&196	&1.11\\\hline
482.sphinx3	&603	&594	&0.98\\\hline
483.xalancbmk	&5101	&4941	&0.96\\\hline
Grand Total	                &42719	&41626	&0.97\\\hline
    \end{tabular}
  \end{center}
  \caption{Number of spills on SPEC2006}
  \label{tab:code-size}
\end{table}

>>>>

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|c|c|}
      \hline
      Metric               & Before & After              \\\hline
      Functions deleted (all callers found)       & 38250   & 38255  \\\hline
      Functions inlined                           & 154986  & 154985 \\\hline
      Spills inserted                             & 50724   & 50784  \\\hline
      LICM
\end{tabular}
  \end{center}
  \caption{Static metrics before and after code-hoisting on \LLVMTestSuite{}}
  \label{tab:static-results}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|c|c|c|}
      \hline
Number of spills  &base(-Ofast) &code-motion(-Ofast) &\%loss \\\hline
400.perlbench	  & 2539	& 2493	& 0.98
401.bzip2	  & 718	        & 707	& 0.98
403.gcc	          & 5782	& 5722	& 0.99
429.mcf	          & 14	        & 17	& 1.21
433.milc	  & 635	        & 642	& 1.01
444.namd	  & 3223	& 3274	& 1.01
445.gobmk	  & 2166	& 2173	& 1.00
447.dealII	  & 11074	& 10234	& 0.92
450.soplex	  & 1122	& 1125	& 1.00
453.povray	  & 4701	& 4692	& 1.09
456.hmmer	  & 1197	& 1274	& 1.06
458.sjeng	  & 168	        & 176	& 1.05
462.libquantum	  & 118	        & 118	& 1
464.h264ref	  & 3379	& 3454	& 1.02
470.lbm	          & 33	        & 33	& 1
471.omnetpp	  & 524	        & 527	& 1.00
473.astar	  & 180	        & 201	& 1.12
482.sphinx3	  & 674	        & 670	& 0.99
483.xalancbmk	  & 5102	& 4965	& 0.97
Grand Total	  & 43349	& 42497	& 0.98
    \end{tabular}
  \end{center}
  \caption{Number of spills on SPEC2006 at -Ofast}
  \label{tab:code-size}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|c|c|c|}
      \hline

Code size         & base(ofast)	& ofast+gvnhoist&	increase in codesize \\\hline
400.perlbench	  &  2469594	& 2478714	& 1.00\\\hline
401.bzip2	  &  865902	& 867502	& 1.00 \\\hline
403.gcc	          &  4379291	& 4437467	& 1.01 \\\hline
429.mcf	          &  794909	& 794749	& 1.00 \\\hline
433.milc	  &  1009553	& 1010209	& 1.00 \\\hline
444.namd	  &  282794	& 286658	& 1.01 \\\hline
445.gobmk	  &  2474193	& 2494673	& 1.01 \\\hline
447.dealII	  &  3577836	& 3605672	& 1.01 \\\hline
450.soplex	  &  411254	& 409034	& 0.99 \\\hline
453.povray	  &  1114405	& 1114241	& 1.00 \\\hline
456.hmmer	  &  1421823	& 1425287	& 1.00 \\\hline
458.sjeng	  &  941066	& 940626	& 1.00 \\\hline
462.libquantum	  &  911028	& 911124	& 1.00 \\\hline
464.h264ref	  &  1677417	& 1680841	& 1.00 \\\hline
470.lbm	          &  795444	& 795444	& 1    \\\hline
471.omnetpp	  &  661099	& 658411	& 0.99 \\\hline
473.astar	  &  44296	& 45224		& 1.02 \\\hline
482.sphinx3	  &  1337445	& 1334437	& 1.00 \\\hline
483.xalancbmk	  &  4293600	& 4247108	& 0.99 \\\hline
    \end{tabular}
  \end{center}
  \caption{Number of spills on SPEC2006 at -Ofast}
  \label{tab:code-size}
\end{table}
